---
title: "10-Load-Data"
output: html_notebook
---

This is the import and filling in blank rows
*change input file*
*change replicate #*
```{r}
testdata=read.csv(file="~/Desktop/analysis_20Aug20/LC3-LAMP_analysis/cleaned_9Sep20/9Sep20_cleaned-NSW3005_basal.csv",header=TRUE)
testdata$BvsS<-"Basal"
testdata$Rep<-3
nobs=nrow(testdata)
for (i in 1:nobs) {
  if (is.na(testdata[i,3])) {
    testdata[i,1]<-fname
    testdata[i,2]<-LC3TotVol
    testdata[i,3]<-LC3puncta
    testdata[i,4]<-LC3mInt
    testdata[i,5]<-Nuc
    testdata[i,6]<-LAMPsumInt
    testdata[i,7]<-LAMPmInt
    testdata[i,8]<-LAMPstInt
    testdata[i,9]<-LAMPTotVol
  } 
  else {
    fname=testdata[i,1]
    LC3TotVol=testdata[i,2]
    LC3puncta=testdata[i,3]
    LC3mInt=testdata[i,4]
    Nuc=testdata[i,5]
    LAMPsumInt=testdata[i,6]
    LAMPmInt=testdata[i,7]
    LAMPstInt=testdata[i,8]
    LAMPTotVol=testdata[i,9]
  }
}

testdata2=read.csv(file="~/Desktop/analysis_20Aug20/LC3-LAMP_analysis/cleaned_9Sep20/9Sep20_cleaned-NSW3005_starved.csv",header=TRUE)
testdata2$BvsS<-"Starved"
testdata2$Rep<-3
nobs=nrow(testdata2)
for (i in 1:nobs) {
  if (is.na(testdata2[i,3])) {
    testdata2[i,1]<-fname
    testdata2[i,2]<-LC3TotVol
    testdata2[i,3]<-LC3puncta
    testdata2[i,4]<-LC3mInt
    testdata2[i,5]<-Nuc
    testdata2[i,6]<-LAMPsumInt
    testdata2[i,7]<-LAMPmInt
    testdata2[i,8]<-LAMPstInt
    testdata2[i,9]<-LAMPTotVol
  } 
  else {
    fname=testdata2[i,1]
    LC3TotVol=testdata2[i,2]
    LC3puncta=testdata2[i,3]
    LC3mInt=testdata2[i,4]
    Nuc=testdata2[i,5]
    LAMPsumInt=testdata2[i,6]
    LAMPmInt=testdata2[i,7]
    LAMPstInt=testdata2[i,8]
    LAMPTotVol=testdata2[i,9]
  }
}
both<-rbind(testdata,testdata2)
```

Basic Calculations
```{r}
both$AverageVolume<-both$LC3TotalObjectVolume/both$LC3punctaCount
both$punctaPerCell<-both$LC3punctaCount/both$NucleiCount
both$TotVolPerCell<-both$LC3TotalObjectVolume/both$NucleiCount
both$TotLAMPIntPerCell<-both$LAMP1SumIntensity/both$NucleiCount
```

Getting 1 row per Filename into a new file "both_nodup", making individual type files, adding total cell counts per type
*If necessary update substring values based on filenames from input document*
```{r}
both_nodup<-both[!duplicated(both$Filename),]
both_nodup$Type<-NA
nboth_nodup<-nrow(both_nodup)
WT<-both_nodup[0,]
Mock<-both_nodup[0,]
Control<-both_nodup[0,]
tepsin<-both_nodup[0,]
AP4E1<-both_nodup[0,]
for (c in 1:nboth_nodup) {
  if (substr(both_nodup[c,1],45,45)=="W") {
    WT<-rbind(WT, both_nodup[c,])
    WT$Type="WT"
    both_nodup$Type[c]<-"WT"
  }
  else if (substr(both_nodup[c,1],45,45)=="M") {
    Mock<-rbind(Mock, both_nodup[c,])
    Mock$Type<-"Mock"
    both_nodup$Type[c]<-"Mock"
  }
  else if (substr(both_nodup[c,1],45,45)=="C") {
    Control<-rbind(Control, both_nodup[c,])
    Control$Type<-"Control"
    both_nodup$Type[c]<-"Control"
  }
  else if (substr(both_nodup[c,1],45,45)=="t") {
    tepsin<-rbind(tepsin, both_nodup[c,])
    tepsin$Type<-"tepsin"
    both_nodup$Type[c]<-"tepsin"
  }
  else {
    AP4E1<-rbind(AP4E1, both_nodup[c,])
    AP4E1$Type<-"AP4E1"
    both_nodup$Type[c]<-"AP4E1"
  }
  
}

```


Get Sum of cell counts per type
```{r}
both_nodup$CellSum<-NA

for (t in c("WT","Mock", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
  both_nodup$CellSum[which(both_nodup$Type==t & both_nodup$BvsS==bs)]<-sum(both_nodup$NucleiCount[which(both_nodup$Type==t & both_nodup$BvsS==bs)])
   }
}
```

Get sum of LC3 puncta counts per condition
*Use when cell counts match!*
```{r}
both_nodup$TotalLC3PunctaCount<-NA

for (t in c("WT","Mock", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
  both_nodup$TotalLC3PunctaCount[which(both_nodup$Type==t & both_nodup$BvsS==bs)]<-sum(both_nodup$LC3punctaCount[which(both_nodup$Type==t & both_nodup$BvsS==bs)])
   }
}
```


Getting average of subsets
```{r}
WT$TypeIntAvg<-mean(WT$MeanIntensity)
WT$TypeAvgVol<-mean(WT$AverageVolume)
WT$TypeAvgpuncta<-mean(WT$punctaPerCell)
WT$TypeLAMPIntAvg<-mean(WT$LAMP1meanInt)
Mock$TypeIntAvg<-mean(Mock$MeanIntensity)
Mock$TypeAvgVol<-mean(Mock$AverageVolume)
Mock$TypeAvgpuncta<-mean(Mock$punctaPerCell)
Mock$TypeLAMPIntAvg<-mean(Mock$LAMP1meanInt)
Control$TypeIntAvg<-mean(Control$MeanIntensity)
Control$TypeAvgVol<-mean(Control$AverageVolume)
Control$TypeAvgpuncta<-mean(Control$punctaPerCell)
Control$TypeLAMPIntAvg<-mean(Control$LAMP1meanInt)
tepsin$TypeIntAvg<-mean(tepsin$MeanIntensity)
tepsin$TypeAvgVol<-mean(tepsin$AverageVolume)
tepsin$TypeAvgpuncta<-mean(tepsin$punctaPerCell)
tepsin$TypeLAMPIntAvg<-mean(tepsin$LAMP1meanInt)
AP4E1$TypeIntAvg<-mean(AP4E1$MeanIntensity)
AP4E1$TypeAvgVol<-mean(AP4E1$AverageVolume)
AP4E1$TypeAvgpuncta<-mean(AP4E1$punctaPerCell)
AP4E1$TypeLAMPIntAvg<-mean(AP4E1$LAMP1meanInt)
```

Make final file

*change file output name*
```{r}
FinalOut<-rbind(WT,Mock,Control,tepsin,AP4E1)
FinalOut<-FinalOut[!duplicated(FinalOut$Type),17:21]
write.csv(FinalOut,"~/Desktop/Starved_11Mar20-dataset_26Mar20_average.csv")
```


