---
title: "11-Load-Individual-Puncta-Data"
output: html_notebook
---

Input CSV file and filling in rows
*change input file name*
*change BvsS type*
*change replicate #*

```{r}
testdata=read.csv(file="~/Desktop/analysis_20Aug20/LC3-LAMP_analysis/cleaned_9Sep20/9Sep20_cleaned-NSW3005_basal.csv",header=TRUE)
testdata$BvsS<-"Basal"
testdata$Rep<-3
nobs=nrow(testdata)
for (i in 1:nobs) {
  if (is.na(testdata[i,3])) {
    testdata[i,1]<-fname
    testdata[i,2]<-LC3TotVol
    testdata[i,3]<-LC3puncta
    testdata[i,4]<-LC3mInt
    testdata[i,5]<-Nuc
    testdata[i,6]<-LAMPsumInt
    testdata[i,7]<-LAMPmInt
    testdata[i,8]<-LAMPstInt
    testdata[i,9]<-LAMPTotVol
  } 
  else {
    fname=testdata[i,1]
    LC3TotVol=testdata[i,2]
    LC3puncta=testdata[i,3]
    LC3mInt=testdata[i,4]
    Nuc=testdata[i,5]
    LAMPsumInt=testdata[i,6]
    LAMPmInt=testdata[i,7]
    LAMPstInt=testdata[i,8]
    LAMPTotVol=testdata[i,9]
  }
}

testdata2=read.csv(file="~/Desktop/analysis_20Aug20/LC3-LAMP_analysis/cleaned_9Sep20/9Sep20_cleaned-NSW3005_starved.csv",header=TRUE)
testdata2$BvsS<-"Starved"
testdata2$Rep<-3
nobs=nrow(testdata2)
for (i in 1:nobs) {
  if (is.na(testdata2[i,3])) {
    testdata2[i,1]<-fname
    testdata2[i,2]<-LC3TotVol
    testdata2[i,3]<-LC3puncta
    testdata2[i,4]<-LC3mInt
    testdata2[i,5]<-Nuc
    testdata2[i,6]<-LAMPsumInt
    testdata2[i,7]<-LAMPmInt
    testdata2[i,8]<-LAMPstInt
    testdata2[i,9]<-LAMPTotVol
  } 
  else {
    fname=testdata2[i,1]
    LC3TotVol=testdata2[i,2]
    LC3puncta=testdata2[i,3]
    LC3mInt=testdata2[i,4]
    Nuc=testdata2[i,5]
    LAMPsumInt=testdata2[i,6]
    LAMPmInt=testdata2[i,7]
    LAMPstInt=testdata2[i,8]
    LAMPTotVol=testdata2[i,9]
  }
}
temp<-rbind(testdata,testdata2)
```

Adding type designation
*if necessary update substring values based on filename in input document*

```{r}
temp$Type<-NA
ntemp<-nrow(temp)


for (c in 1:ntemp) {
  if (substr(temp[c,1],45,45)=="W") {
    temp$Type[c]<-"WT"
  }
  else if (substr(temp[c,1],45,45)=="M") {
    temp$Type[c]<-"Mock"
  }
  else if (substr(temp[c,1],45,45)=="C") {
    temp$Type[c]<-"Control"
  }
  else if (substr(temp[c,1],45,45)=="t") {
    temp$Type[c]<-"tepsin"
  }
  else {
    temp$Type[c]<-"AP4E1"
  }
  
}
temp$Type<-factor(temp$Type, levels=c("WT", "Mock", "Control", "tepsin", "AP4E1"))
```

Calculating Summary Statistics
```{r}
temp$IndeVolVar<-NA
temp$IndeVolMean<-NA
temp$IndeVolSTD<-NA
temp$IndeVolMed<-NA

temp$BvsS<-factor(temp$BvsS, levels=c("Basal", "Starved"))

for (t in c("WT","Mock", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
  temp$IndeVolMean[which(temp$Type==t & temp$BvsS==bs)]<-mean(temp$LC3Volume[which(temp$Type==t & temp$BvsS==bs)],na.rm = T)
   
  temp$IndeVolMed[which(temp$Type==t & temp$BvsS==bs)]<-median(temp$LC3Volume[which(temp$Type==t & temp$BvsS==bs)],na.rm = T)
  
  temp$IndeVolVar[which(temp$Type==t & temp$BvsS==bs)]<-var(temp$LC3Volume[which(temp$Type==t & temp$BvsS==bs)],na.rm = T)
  
  temp$IndeVolSTD[which(temp$Type==t & temp$BvsS==bs)]<-sd(temp$LC3Volume[which(temp$Type==t & temp$BvsS==bs)],na.rm = T)
 
   }
}
```


calculating number of enlarged puncta

```{r}
temp$EnlargedPunctaCount<-NA

temp$BvsS<-factor(temp$BvsS, levels=c("Basal", "Starved"))

for (t in c("WT","Mock", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
    temp$EnlargedPunctaCount[which(temp$Type==t & temp$BvsS==bs)]<-length(which(temp$Type==t & temp$BvsS==bs & temp$LC3Volume >2))
  }
}

```

Average volume of enlarged puncta
```{r}
temp$EnlargedPunctaAveVol<-NA

temp$BvsS<-factor(temp$BvsS, levels=c("Basal", "Starved"))

for (t in c("WT","Mock", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
    temp$EnlargedPunctaAveVol[which(temp$Type==t & temp$BvsS==bs)]<-sum(temp$LC3Volume[which(temp$Type==t & temp$BvsS==bs & temp$LC3Volume >2)])/length(which(temp$Type==t & temp$BvsS==bs & temp$LC3Volume >2))
  }
}

```


Log10 of data values
```{r}
temp$LogLC3Volume<-NA
temp$LogLC3MOC<-NA

temp$LogLC3Volume<-log10(temp$LC3Volume)
temp$LogLC3MOC<-log10(temp$MandersLC3MOC)
```

remove NA rows and remove duplicate values
*only use after finished with individual puncta values to assess: total puncta and percent enlarged puncta*
```{r}
tempTotals<-temp[complete.cases(test),]
tempTotals_nodup<-tempTotals[!duplicated(tempTotals$Filename),]
```

Get sum of LC3 puncta counts per condition
*Use when cell counts match!*
```{r}
tempTotals_nodup$TotalLC3PunctaCount<-NA

for (t in c("WT","Mock", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
  tempTotals_nodup$TotalLC3PunctaCount[which(tempTotals_nodup$Type==t & tempTotals_nodup$BvsS==bs)]<-sum(tempTotals_nodup$LC3punctaCount[which(tempTotals_nodup$Type==t & tempTotals_nodup$BvsS==bs)])
   }
}
```


DELETE
CSV import
*change input file path*
```{r}
WBdata=read.csv(file="~/Desktop/analysis_20Aug20/LC3-LAMP_analysis/cleaned_9Sep20/Calculated-PercEnlarged-AveVolEnlarged_17Sep20.csv",header=TRUE)
```

Calculate mean for each condition
```{r}
WBdata$PercEnlargedAve<-NA
WBdata$AveEnlargedVolAve<-NA

for (t in c("WT", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
  WBdata$PercEnlargedAve[which(WBdata$type==t & WBdata$BvsS==bs)]<-sum(WBdata$PercEnlarged[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$PercEnlarged)])/length(which(WBdata$type==t & WBdata$BvsS==bs & WBdata$PercEnlarged))
 
  WBdata$AveEnlargedVolAve[which(WBdata$type==t & WBdata$BvsS==bs)]<-sum(WBdata$AveVolEnlarged[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$AveVolEnlarged)])/length(which(WBdata$type==t & WBdata$BvsS==bs & WBdata$AveVolEnlarged))
  
   }
}


```

Calculate standard deviation for each condition
```{r}
WBdata$PercEnlSD<-NA
WBdata$AveEnlVolSD<-NA


for (t in c("WT", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
  WBdata$PercEnlSD[which(WBdata$type==t & WBdata$BvsS==bs)]<-sd(WBdata$PercEnlarged[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$PercEnlarged)])
 
  WBdata$AveEnlVolSD[which(WBdata$type==t & WBdata$BvsS==bs)]<-sd(WBdata$AveVolEnlarged[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$AveVolEnlarged)])
  
   }
}
```

Remove duplicate rows from replicates
```{r}
WBdata_nodup<-WBdata[!duplicated(WBdata$PercEnlargedAve),]
```

