---
title: "13-Load-Western-quantification"
output: html_notebook
---

CSV import
*change input file path*
```{r}
WBdata=read.csv(file="~/Desktop/BafA_analysis_12May21/BafA_HeLa-KD_gel1_quant_12May21.csv",header=TRUE)

```

standard KD quantification:
-Calculate mean for each condition
```{r}
WBdata$LC3ratioAve<-NA
WBdata$LC3ratioNormAve<-NA
WBdata$LC3IItotAve<-NA
WBdata$LC3IIAve<-NA
WBdata$LC3totAve<-NA
WBdata$tepsinKDAve<-NA
WBdata$AP4EKDAve<-NA

for (t in c("WT", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
  WBdata$LC3ratioAve[which(WBdata$type==t & WBdata$BvsS==bs)]<-sum(WBdata$LC3ratio[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$LC3ratio)])/length(which(WBdata$type==t & WBdata$BvsS==bs & WBdata$LC3ratio))
  
  WBdata$LC3ratioNormAve[which(WBdata$type==t & WBdata$BvsS==bs)]<-sum(WBdata$LC3ratioNorm[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$LC3ratioNorm)])/length(which(WBdata$type==t & WBdata$BvsS==bs & WBdata$LC3ratioNorm))
  
  WBdata$LC3IItotAve[which(WBdata$type==t & WBdata$BvsS==bs)]<-sum(WBdata$LC3IItot[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$LC3IItot)])/length(which(WBdata$type==t & WBdata$BvsS==bs & WBdata$LC3IItot))
  
   WBdata$LC3IIAve[which(WBdata$type==t & WBdata$BvsS==bs)]<-sum(WBdata$LC3II[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$LC3II)])/length(which(WBdata$type==t & WBdata$BvsS==bs & WBdata$LC3II))
  
  WBdata$LC3totAve[which(WBdata$type==t & WBdata$BvsS==bs)]<-sum(WBdata$LC3tot[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$LC3tot)])/length(which(WBdata$type==t & WBdata$BvsS==bs & WBdata$LC3tot))
 
  WBdata$tepsinKDAve[which(WBdata$type==t & WBdata$BvsS==bs)]<-sum(WBdata$tepsinKD[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$tepsinKD)])/length(which(WBdata$type==t & WBdata$BvsS==bs & WBdata$tepsinKD))
  
  WBdata$AP4EKDAve[which(WBdata$type==t & WBdata$BvsS==bs)]<-sum(WBdata$AP4EKD[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$AP4EKD)])/length(which(WBdata$type==t & WBdata$BvsS==bs & WBdata$AP4EKD))
  
   }
}


```

standard KD quantification: 
-Calculate standard deviation for each condition
```{r}
WBdata$LC3ratioSD<-NA
WBdata$LC3ratioNormSD<-NA
WBdata$LC3IItotSD<-NA
WBdata$LC3IISD<-NA
WBdata$LC3totSD<-NA
WBdata$tepsinKDSD<-NA
WBdata$AP4EKDSD<-NA

for (t in c("WT", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
  WBdata$LC3ratioSD[which(WBdata$type==t & WBdata$BvsS==bs)]<-sd(WBdata$LC3ratio[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$LC3ratio)])
 
  WBdata$LC3ratioNormSD[which(WBdata$type==t & WBdata$BvsS==bs)]<-sd(WBdata$LC3ratioNorm[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$LC3ratioNorm)])
  
  WBdata$LC3IItotSD[which(WBdata$type==t & WBdata$BvsS==bs)]<-sd(WBdata$LC3IItot[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$LC3IItot)])
  
  WBdata$LC3IISD[which(WBdata$type==t & WBdata$BvsS==bs)]<-sd(WBdata$LC3II[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$LC3II)])
  
  WBdata$LC3totSD[which(WBdata$type==t & WBdata$BvsS==bs)]<-sd(WBdata$LC3tot[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$LC3tot)])
  
  WBdata$tepsinKDSD[which(WBdata$type==t & WBdata$BvsS==bs)]<-sd(WBdata$tepsinKD[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$tepsinKD)])
  
  WBdata$AP4EKDSD[which(WBdata$type==t & WBdata$BvsS==bs)]<-sd(WBdata$AP4EKD[which(WBdata$type==t & WBdata$BvsS==bs & WBdata$AP4EKD)])
  
   }
}
```

Remove duplicate rows from replicates
```{r}
WBdata_nodup<-WBdata[!duplicated(WBdata$LC3ratioAve),]
```


Following codes optimized for BafA HeLa experiments

BafA KD quantification:
-Calculate mean for each condition
```{r}
WBdata$LC3ratioNormAve<-NA
WBdata$LC3IAve<-NA
WBdata$LC3IIAve<-NA
WBdata$LC3totAve<-NA
WBdata$tepsinKDAve<-NA
WBdata$AP4EKDAve<-NA

for (t in c("WT", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
    for (baf in c("Y", "N")) {
 
  WBdata$LC3ratioNormAve[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf)]<-sum(WBdata$LC3ratioFC[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$LC3ratioFC)])/length(WBdata$LC3ratioFC[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$LC3ratioFC)])
  
  WBdata$LC3IAve[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf)]<-sum(WBdata$relLC3I[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$relLC3I)])/length(which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$relLC3I))
  
   WBdata$LC3IIAve[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf)]<-sum(WBdata$relLC3II[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$relLC3II)])/length(which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$relLC3II))
  
  WBdata$LC3totAve[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf)]<-sum(WBdata$relTotLC3[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$relTotLC3)])/length(which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$relTotLC3))
 
  WBdata$tepsinKDAve[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf)]<-sum(WBdata$relTepsin[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$relTepsin)])/length(which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$relTepsin))
  
  WBdata$AP4EKDAve[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf)]<-sum(WBdata$relEpsilon[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$relEpsilon)])/length(which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$relEpsilon))
  
   }
}
  }

```

BafA KD quantification: 
-Calculate standard deviation for each condition
```{r}
WBdata$LC3ratioNormSD<-NA
WBdata$LC3ISD<-NA
WBdata$LC3IISD<-NA
WBdata$LC3totSD<-NA
WBdata$tepsinKDSD<-NA
WBdata$AP4EKDSD<-NA

for (t in c("WT", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
    for (baf in c("Y", "N")) {
 
  WBdata$LC3ratioNormSD[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf)]<-sd(WBdata$LC3ratioFC[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$LC3ratioFC)])
  
  WBdata$LC3ISD[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf )]<-sd(WBdata$relLC3I[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$relLC3I)])
  
  WBdata$LC3IISD[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf)]<-sd(WBdata$relLC3II[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$relLC3II)])
  
  WBdata$LC3totSD[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf)]<-sd(WBdata$relTotLC3[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$relTotLC3)])
  
  WBdata$tepsinKDSD[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf)]<-sd(WBdata$relTepsin[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$relTepsin)])
  
  WBdata$AP4EKDSD[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf)]<-sd(WBdata$relEpsilon[which(WBdata$Type==t & WBdata$BvsS==bs & WBdata$BafA==baf & WBdata$relEpsilon)])
  
   }
  }
}
```

Remove duplicate rows from replicates
```{r}
WBdata_nodup<-WBdata[!duplicated(WBdata$LC3ratioNormAve),]
```




