---
title: "15-Load-Segmented-Cell-Data"
output: html_notebook
---

CSV import - Mac
*change input file path*
```{r}
testdata=read.csv(file="~/Desktop/EqCellSum_22Feb21/Final/NSW3010_EqCellSum_Basal_count_24Feb21.csv",header=TRUE)
testdata$BvsS<-"Basal"
testdata$Rep<-1
nobs=nrow(testdata)
for (i in 1:nobs) {
  if (testdata[i,1]=="") {
    testdata[i,1]<-fname

  } 
  else {
    fname=testdata[i,1]

  }
}

testdata2=read.csv(file="~/Desktop/EqCellSum_22Feb21/Final/NSW3010_EqCellSum_Starved_count_23Feb21.csv",header=TRUE)
testdata2$BvsS<-"Starved"
testdata2$Rep<-1
nobs=nrow(testdata2)
for (i in 1:nobs) {
  if (testdata2[i,1]=="") {
    testdata2[i,1]<-fname

  } 
  else {
    fname=testdata2[i,1]

  }
}

temp<-rbind(testdata,testdata2)
```

CSV import - *Windows*
*MUST HAVE FILES IN R PROJECT WD* 
*change input file path*
```{r}
testdata=read.csv(file="./Analysis-files/eqCellsum_analysis/NSW3012_EqCellSum_Basal_count_23Feb21.csv",header=TRUE)
testdata$BvsS<-"Basal"
testdata$Rep<-2
nobs=nrow(testdata)
for (i in 1:nobs) {
  if (testdata[i,1]=="") {
    testdata[i,1]<-fname

  } 
  else {
    fname=testdata[i,1]

  }
}

testdata2=read.csv(file="./Analysis-files/eqCellsum_analysis/NSW3012_EqCellSum_Starved_count_22Feb21.csv",header=TRUE)
testdata2$BvsS<-"Starved"
testdata2$Rep<-2
nobs=nrow(testdata2)
for (i in 1:nobs) {
  if (testdata2[i,1]=="") {
    testdata2[i,1]<-fname

  } 
  else {
    fname=testdata2[i,1]

  }
}

temp<-rbind(testdata,testdata2)
```


Adding type designation
*if necessary update substring values based on filename in input document*
```{r}
temp$Type<-NA
ntemp<-nrow(temp)


for (c in 1:ntemp) {
  if (substr(temp[c,1],45,45)=="W") {
    temp$Type[c]<-"WT"
  }
  else if (substr(temp[c,1],45,45)=="C") {
    temp$Type[c]<-"Control"
  }
  else if (substr(temp[c,1],45,45)=="t") {
    temp$Type[c]<-"tepsin"
  }
  else {
    temp$Type[c]<-"AP4E1"
  }
  
}
temp$Type<-factor(temp$Type, levels=c("WT", "Control", "tepsin", "AP4E1"))
```

Find files where number of Nuclei does not match number of segmented cells (based on LAMPCellID):

These files should be evaluated to identify images where cells were not segmented properly as all cells should have LAMP1 signal. 
*added condition to ignore NA values in LAMP counts column, must check for presence of na values with is.na function to and manually note these erroneous images*
```{r}
ntemp<-nrow(temp)
temp[,2]<-as.numeric(temp[,2])
temp[,5]<-as.numeric(temp[,5])
ncell<-temp[1,2]
rs<-c()
for (i in 1:ntemp) {
  if (!is.na(temp[i,2]) & i!=1) {
    if (!is.na(temp[i-1,5]) & ncell!=temp[i-1,5]) {
      rs<-c(rs,i-1)
    }
    ncell<-temp[i,2]
  }
  
  if (i==ntemp){
    if (ncell!=temp[i,5]) {
      rs<-c(rs,i)
    }
  }
}

badcellc<-data.frame(temp[rs,1])
```

It is possible some cells will have no LC3 puncta. But all cells should have LAMP1. This function will replace NA rows in the LC3 Puncta Count column with 0 so they will be acknowledged in the data analysis
```{r}
temp[is.na(temp[,4]),4]<-0
```

Get Sum of cell counts per type
```{r}
temp$CellSum<-NA
ntemp<-nrow(temp)

for (t in c("WT", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
    for (r in c("1", "2","3")) {
      
       temp$CellSum[which(temp$Type==t & temp$BvsS==bs & temp$Rep==r)]<-sum(temp$NucleiCount[which(temp$Type==t & temp$BvsS==bs &temp$Rep==r)],na.rm = TRUE)
   
    }
  }
}
```

Apply Min-Max normalization to data
```{r}
temp$LC3CountMinMax<-NA
ntemp<-nrow(temp)


norm_minmax <- function(x){
                (x-min(x))/(max(x)-min(x))
}

  temp$LC3CountMinMax<-norm_minmax(temp$LC3PunctaCount)
  

```

calculating number of cells with counts above WT 3rd quartile (independently determined for basal and starved 3rd quartilerep3C)

```{r}
temp$cellsHighCount<-NA


temp$BvsS<-factor(temp$BvsS, levels=c("Basal", "Starved"))

for (t in c("WT","Mock", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
    x=quantile(temp$LC3CountMinMax[which(temp$Type=="WT" & temp$BvsS==bs)], probs=0.75)
    temp$cellsHighCount[which(temp$Type==t & temp$BvsS==bs)]<-length(which(temp$Type==t & temp$BvsS==bs & temp$LC3CountMinMax >x))
  }
}

```

Generate dataframe of non duplicated data for number of cells with high puncta counts
#sorts for no duplicates based on type,BvsS, and high count
```{r}
HighCount_nodup<-temp[!duplicated(temp[,c(7,9,13)]),]

```


High count data no duplicate data will need to have summary averages and SD calculated. Once all the no-duplicate dataframes for each replicate have been generated with the functions above, they should be bound together using the rbind function. This complete data set should be used for the following calculations of mean and sd
```{r}
HighCount$HiCountAve<-NA
HighCount$HiCountSD<-NA

for (t in c("WT", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
  HighCount$HiCountAve[which(HighCount$Type==t & HighCount$BvsS==bs)]<-sum(HighCount$cellsHighCount[which(HighCount$Type==t & HighCount$BvsS==bs & HighCount$cellsHighCount)])/length(which(HighCount$Type==t & HighCount$BvsS==bs & HighCount$cellsHighCount))

  HighCount$HiCountSD[which(HighCount$Type==t & HighCount$BvsS==bs)]<-sd(HighCount$cellsHighCount[which(HighCount$Type==t & HighCount$BvsS==bs & HighCount$cellsHighCount)])
  }
  }
```



print list of images with high LC3 puncta counts to find image artifacts
```{r}

ntemp<-nrow(temp)
temp$BvsS<-factor(temp$BvsS, levels=c("Basal", "Starved"))
img<-c()

for (i in 1:ntemp) {
  if (!is.na(temp[i,4]) & temp[i,4]>150) {
    img<-c(img,i)
  }
}

HighCounts<-data.frame(temp[img,])

```

find mean count/cell per type
```{r}
temp$meanCount<-NA
ntemp<-nrow(temp)

for (t in c("WT", "Control", "tepsin", "AP4E1")) {
  for (bs in c("Basal", "Starved")) {
    for (r in c("1", "2","3")) {
      
       temp$meanCount[which(temp$Type==t & temp$BvsS==bs & temp$Rep==r)]<-mean(temp$LC3PunctaCount[which(temp$Type==t & temp$BvsS==bs &temp$Rep==r)],na.rm = TRUE)
   
    }
  }
}
```

print list of images with near mean values
```{r}

ntemp<-nrow(temp)
temp$BvsS<-factor(temp$BvsS, levels=c("Basal", "Starved"))
img<-c()

for (i in 1:ntemp) {
  if (!is.na(temp[i,4]) & temp[i,4]>150) {
    img<-c(img,i)
  }
}

HighCounts<-data.frame(temp[img,])

```
