---
title: "16-Load-Seg-Ind-Puncta-Data"
output: html_notebook
---
CSV import - Mac
*change input file path*
```{r}
testdata=read.csv(file="~/Desktop/21Jan21_analysis/final/NSW3016_Basal_Vol-Int_15Feb21.csv",header=TRUE)
testdata$BvsS<-"Basal"
testdata$Rep<-3
nobs=nrow(testdata)
for (i in 1:nobs) {
  if (testdata[i,1]=="") {
    testdata[i,1]<-fname
    

  } 
  else {
    fname=testdata[i,1]
  }
}

testdata2=read.csv(file="~/Desktop/21Jan21_analysis/final/NSW3016_Starved_Vol-Int_15Feb21.csv",header=TRUE)
testdata2$BvsS<-"Starved"
testdata2$Rep<-3
nobs=nrow(testdata2)
for (i in 1:nobs) {
  if (testdata2[i,1]=="") {
    testdata2[i,1]<-fname

  } 
  else {
    fname=testdata2[i,1]

  }
}

temp<-rbind(testdata,testdata2)
```

CSV import - *Windows*
*MUST HAVE FILES IN R PROJECT WD* 
*change input file path*
```{r}
testdata=read.csv(file="./Analysis-files/eqCellsum_analysis/NSW3010_EqCellSum_Basal_count_24Feb21.csv",header=TRUE)
testdata$BvsS<-"Basal"
testdata$Rep<-1
nobs=nrow(testdata)
for (i in 1:nobs) {
  if (testdata[i,1]=="") {
    testdata[i,1]<-fname

  } 
  else {
    fname=testdata[i,1]

  }
}

testdata2=read.csv(file="./Analysis-files/eqCellsum_analysis/NSW3010_EqCellSum_Starved_count_24Feb21.csv",header=TRUE)
testdata2$BvsS<-"Starved"
testdata2$Rep<-1
nobs=nrow(testdata2)
for (i in 1:nobs) {
  if (testdata2[i,1]=="") {
    testdata2[i,1]<-fname

  } 
  else {
    fname=testdata2[i,1]

  }
}

temp<-rbind(testdata,testdata2)
```


Adding type designation
*if necessary update substring values based on filename in input document*
```{r}
temp$Type<-NA
ntemp<-nrow(temp)


for (c in 1:ntemp) {
  if (substr(temp[c,1],45,45)=="W") {
    temp$Type[c]<-"WT"
  }
  else if (substr(temp[c,1],45,45)=="C") {
    temp$Type[c]<-"Control"
  }
  else if (substr(temp[c,1],45,45)=="t") {
    temp$Type[c]<-"tepsin"
  }
  else {
    temp$Type[c]<-"AP4E1"
  }
  
}
temp$Type<-factor(temp$Type, levels=c("WT", "Control", "tepsin", "AP4E1"))
```

Getting average or sum values per cell for LC3 metrics
```{r}
ntemp<-nrow(temp)
temp[,2]<-as.numeric(temp[,2])
temp$AveLC3VolPerCell <- NA
temp$AveLC3IntPerCell<- NA
temp$AveLC3SumIntPerCell<-NA
temp$TotLC3IntPerCell<-NA
rs<-c()
cid<-1
fname<-temp[1,1]
for (i in 1:ntemp) {
  if (!is.na(temp[i,2])){
    if (temp[i,2]!=cid | temp[i,1]!=fname) {
      temp$AveLC3VolPerCell[rs]<-mean(temp$LC3PunctaVol[rs])
      temp$AveLC3IntPerCell[rs]<-mean(temp$LC3PunctaMeanInt[rs])
      temp$AveLC3SumIntPerCell[rs]<-mean(temp$LC3SumObjInt[rs])
      temp$TotLC3IntPerCell[rs]<-sum(temp$LC3SumObjInt[rs])
      rs<-c(i)
      cid<-temp[i,2]
      fname<-temp[i,1]
    }
    else {
      rs<-c(rs,i)
    }
  }
  if (i==ntemp){
    temp$AveLC3VolPerCell[rs]<-mean(temp$LC3PunctaVol[rs])
    temp$AveLC3IntPerCell[rs]<-mean(temp$LC3PunctaMeanInt[rs])
    temp$AveLC3SumIntPerCell[rs]<-mean(temp$LC3SumObjInt[rs])
    temp$TotLC3IntPerCell[rs]<-sum(temp$LC3SumObjInt[rs])
  }
}
```

Getting average or sum values per cell for LAMP1 metrics
```{r}
ntemp<-nrow(temp)
temp[,6]<-as.numeric(temp[,6])
temp$AveLAMPVolPerCell <- NA
temp$AveLAMPIntPerCell<- NA
temp$AveLAMPSumIntPerCell<-NA
temp$TotLAMPIntPerCell<-NA
rs<-c()
cid<-1
fname<-temp[1,1]
for (i in 1:ntemp) {
  if (!is.na(temp[i,6])){
    if (temp[i,6]!=cid | temp[i,1]!=fname) {
      temp$AveLAMPVolPerCell[rs]<-mean(temp$LAMPObjVol[rs])
      temp$AveLAMPIntPerCell[rs]<-mean(temp$LAMPMeanObjInt[rs])
      temp$AveLAMPSumIntPerCell[rs]<-mean(temp$LAMPSumObjInt[rs])
      temp$TotLAMPIntPerCell[rs]<-sum(temp$LAMPSumObjInt[rs])
      rs<-c(i)
      cid<-temp[i,6]
      fname<-temp[i,1]
    }
    else {
      rs<-c(rs,i)
    }
  }
  if (i==ntemp){
    temp$AveLAMPVolPerCell[rs]<-mean(temp$LAMPObjVol[rs])
    temp$AveLAMPIntPerCell[rs]<-mean(temp$LAMPMeanObjInt[rs])
    temp$AveLAMPSumIntPerCell[rs]<-mean(temp$LAMPSumObjInt[rs])
    temp$TotLAMPIntPerCell[rs]<-sum(temp$LAMPSumObjInt[rs])
  }
}
```

Removing unnecessary columns and duplicate rows to have values per cell
*LC3; also renames CellID column to prepare for merging*
```{r}
LC3noDup<-temp[!duplicated(temp[,c(1,2,13,14)]),c(1,2,10,11,12,13,14,15,16)]
LC3noDup<-LC3noDup[which(!is.na(LC3noDup[,2])),]
names(LC3noDup)[names(LC3noDup)=="LC3CellID"]<-"CellID"
```

Removing unnecessary columns and duplicate rows to have values per cell
*LAMP; also renames CellID column to prepare for merging*
```{r}
LAMPnoDup<-temp[!duplicated(temp[,c(1,6)]),c(1,6,10,11,12,17,18,19,20)]
LAMPnoDup<-LAMPnoDup[which(!is.na(LAMPnoDup[,8])),]
names(LAMPnoDup)[names(LAMPnoDup)=="LAMPCellID"]<-"CellID"
```

Merging LC3 and LAMP cleaned data frames for graphing
*replaces NA values with 0 if desired*
```{r}
test <- merge(LC3noDup,LAMPnoDup, all = TRUE)
#test[is.na(test)]<-0
```

Option to merge per cell metrics with object counts per cell dataframe
```{r}
test2 <- merge(test,counts, all = TRUE)
```

print list of images with high LC3 intensity
```{r}

ntemp<-nrow(temp)
temp$BvsS<-factor(temp$BvsS, levels=c("Basal", "Starved"))
img<-c()

for (i in 1:ntemp) {
  if (!is.na(temp[i,9]) & temp[i,9]>20000000) {
    img<-c(img,i-1)
  }
}

brightCells<-data.frame(temp[img,])

```

