---
title: "30-Statistical-Analysis"
output: html_notebook
---


Kruskal-Wallis Test of object counts; separate Basal vs Starved analysis
*multiple replicates*
```{r}
#to test segmentation of dataset
#subsetB<-temp[temp$BvsS == "Basal",]

#Basal

#KW_LC3CountsBasal<-kruskal_test(LC3PunctaCount~Type, data=temp[temp$BvsS == "Basal",])
#summary(KW_LC3CountsBasal)
#dunn_test(LC3PunctaCount~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

KW_LC3CountsMMbasal<-kruskal_test(LC3CountMinMax~Type, data=temp[temp$BvsS == "Basal",])
summary(KW_LC3CountsMMbasal)
dt_LC3Countb<-dunn_test(LC3CountMinMax~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

#Starved

#KW_LC3CountsStarved<-kruskal_test(LC3PunctaCount~Type, data=temp[temp$BvsS == "Starved",])
#summary(KW_LC3CountsStarved)
#dunn_test(LC3PunctaCount~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

KW_LC3CountsMMstarved<-kruskal_test(LC3CountMinMax~Type, data=temp[temp$BvsS == "Starved",])
summary(KW_LC3CountsMMstarved)
dt_LC3Counts<-dunn_test(LC3CountMinMax~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

```
U-Test of object Counts
*for nonparametric distributions*
```{r}
for (t in c("WT", "Control", "tepsin", "AP4E1")) {
    ds<-wilcox_test(data=temp[which(temp$Type==t),], LC3CountMinMax~BvsS, paired = FALSE)
   assign(paste(t,"LC3CountMinMax",sep="_"),ds)
}

LC3CountuTest<-rbind(WT_LC3CountMinMax,Control_LC3CountMinMax,tepsin_LC3CountMinMax,AP4E1_LC3CountMinMax)

```

U-Test of individual Obj measurements
*for nonparametric distributions*
```{r}

for (t in c("WT", "Control", "tepsin", "AP4E1")) {
  for (x in c("LC3VolMinMax","LC3IntMinMax","LC3SumIntMinMax","LC3totIntMinMax","LAMPVolMinMax","LAMPIntMinMax","LAMPSumIntMinMax","LAMPtotIntMinMax")){
    ds<-wilcox_test(data=temp[which(temp$Type==t),], as.formula(paste(x,"BvsS",sep="~")), paired = FALSE)
    assign(paste(t,x,sep="_"),ds)
    
  }
}

LC3VoluTest<-rbind(WT_LC3VolMinMax,Control_LC3VolMinMax,tepsin_LC3VolMinMax,AP4E1_LC3VolMinMax)
LC3IntuTest<-rbind(WT_LC3IntMinMax,Control_LC3IntMinMax,tepsin_LC3IntMinMax,AP4E1_LC3IntMinMax)
LC3SumIntuTest<-rbind(WT_LC3SumIntMinMax,Control_LC3SumIntMinMax,tepsin_LC3SumIntMinMax,AP4E1_LC3SumIntMinMax)
LC3TotIntuTest<-rbind(WT_LC3totIntMinMax,Control_LC3totIntMinMax,tepsin_LC3totIntMinMax,AP4E1_LC3totIntMinMax)

LAMPVoluTest<-rbind(WT_LAMPVolMinMax,Control_LAMPVolMinMax,tepsin_LAMPVolMinMax,AP4E1_LAMPVolMinMax)
LAMPIntuTest<-rbind(WT_LAMPIntMinMax,Control_LAMPIntMinMax,tepsin_LAMPIntMinMax,AP4E1_LAMPIntMinMax)
LAMPSumIntuTest<-rbind(WT_LAMPSumIntMinMax,Control_LAMPSumIntMinMax,tepsin_LAMPSumIntMinMax,AP4E1_LAMPSumIntMinMax)
LAMPTotIntuTest<-rbind(WT_LAMPtotIntMinMax,Control_LAMPtotIntMinMax,tepsin_LAMPtotIntMinMax,AP4E1_LAMPtotIntMinMax)

```

Export csv files of compiled U-Test stats data
```{r}
#LC3
write.csv(LC3CountuTest, file= "./Analysis-files/eqCellsum_analysis/stats/LC3CountuTest_1Jun21.csv")

write.csv(LC3VoluTest, file= "./Analysis-files/eqCellsum_analysis/stats/LC3VoluTest_1Jun21.csv")

write.csv(LC3IntuTest, file= "./Analysis-files/eqCellsum_analysis/stats/LC3IntuTest_1Jun21.csv")

write.csv(LC3SumIntuTest, file= "./Analysis-files/eqCellsum_analysis/stats/LC3SumIntuTest_1Jun21.csv")

write.csv(LC3TotIntuTest, file= "./Analysis-files/eqCellsum_analysis/stats/LC3TotIntuTest_1Jun21.csv")


#LAMP
write.csv(LAMPVoluTest, file= "./Analysis-files/eqCellsum_analysis/stats/LAMPVoluTest_1Jun21.csv")

write.csv(LAMPIntuTest, file= "./Analysis-files/eqCellsum_analysis/stats/LAMPIntuTest_1Jun21.csv")

write.csv(LAMPSumIntuTest, file= "./Analysis-files/eqCellsum_analysis/stats/LAMPSumIntuTest_1Jun21.csv")

write.csv(LAMPTotIntuTest, file= "./Analysis-files/eqCellsum_analysis/stats/LAMPTotIntuTest_1Jun21.csv")

```




Kruskal-Wallis Test of ind puncta measurements; separate Basal vs Starved analysis
*NONPARAMETRIC DATA**multiple replicates*
```{r}
#to test segmentation of dataset
#subsetB<-temp[temp$BvsS == "Basal",]

#Basal
#KW_LC3Volb<-kruskal_test(AveLC3VolPerCell~Type, data=temp[temp$BvsS == "Basal",])
#summary(KW_LC3Volb)
#dunn_test(AveLC3VolPerCell~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

KW_LC3VolMMb<-kruskal_test(LC3VolMinMax~Type, data=temp[temp$BvsS == "Basal",])
summary(KW_LC3VolMMb)
dt_LC3Volb<-dunn_test(LC3VolMinMax~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

#KW_LC3Intb<-kruskal_test(AveLC3IntPerCell~Type, data=temp[temp$BvsS == "Basal",])
#summary(KW_LC3Intb)
#dunn_test(AveLC3IntPerCell~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

KW_LC3IntMMb<-kruskal_test(LC3IntMinMax~Type, data=temp[temp$BvsS == "Basal",])
summary(KW_LC3IntMMb)
dt_LC3Intb<-dunn_test(LC3IntMinMax~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

#KW_LC3SumIntb<-kruskal_test(AveLC3SumIntPerCell~Type, data=temp[temp$BvsS == "Basal",])
#summary(KW_LC3SumIntb)
#dunn_test(AveLC3SumIntPerCell~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

KW_LC3SumIntMMb<-kruskal_test(LC3SumIntMinMax~Type, data=temp[temp$BvsS == "Basal",])
summary(KW_LC3SumIntMMb)
dt_LC3SumIntb<-dunn_test(LC3SumIntMinMax~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

#KW_LC3totIntb<-kruskal_test(TotLC3IntPerCell~Type, data=temp[temp$BvsS == "Basal",])
#summary(KW_LC3totIntb)
#dunn_test(TotLC3IntPerCell~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

KW_LC3totIntMMb<-kruskal_test(LC3totIntMinMax~Type, data=temp[temp$BvsS == "Basal",])
summary(KW_LC3totIntMMb)
dt_LC3totIntb<-dunn_test(LC3totIntMinMax~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

#KW_LAMPVolb<-kruskal_test(AveLAMPVolPerCell~Type, data=temp[temp$BvsS == "Basal",])
#summary(KW_LAMPVolb)
#dunn_test(AveLAMPVolPerCell~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

KW_LAMPVolMMb<-kruskal_test(LAMPVolMinMax~Type, data=temp[temp$BvsS == "Basal",])
summary(KW_LAMPVolMMb)
dt_LAMPVolb<-dunn_test(LAMPVolMinMax~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

#KW_LAMPIntb<-kruskal_test(AveLAMPIntPerCell~Type, data=temp[temp$BvsS == "Basal",])
#summary(KW_LAMPIntb)
#dunn_test(AveLAMPIntPerCell~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

KW_LAMPIntMMb<-kruskal_test(LAMPIntMinMax~Type, data=temp[temp$BvsS == "Basal",])
summary(KW_LAMPIntMMb)
dt_LAMPIntb<-dunn_test(LAMPIntMinMax~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

#KW_LAMPSumIntb<-kruskal_test(AveLAMPSumIntPerCell~Type, data=temp[temp$BvsS == "Basal",])
#summary(KW_LAMPSumIntb)
#dunn_test(AveLAMPSumIntPerCell~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

KW_LAMPSumIntMMb<-kruskal_test(LAMPSumIntMinMax~Type, data=temp[temp$BvsS == "Basal",])
summary(KW_LAMPSumIntMMb)
dt_LAMPSumIntb<-dunn_test(LAMPSumIntMinMax~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

#KW_LAMPtotIntb<-kruskal_test(TotLAMPIntPerCell~Type, data=temp[temp$BvsS == "Basal",])
#summary(KW_LAMPtotIntb)
#dunn_test(TotLAMPIntPerCell~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")

KW_LAMPtotIntMMb<-kruskal_test(LAMPtotIntMinMax~Type, data=temp[temp$BvsS == "Basal",])
summary(KW_LAMPtotIntMMb)
dt_LAMPtotIntb<-dunn_test(LAMPtotIntMinMax~Type, data=temp[temp$BvsS == "Basal",], p.adjust.method = "bonferroni")



#Starved

#KW_LC3Volb<-kruskal_test(AveLC3VolPerCell~Type, data=temp[temp$BvsS == "Starved",])
#summary(KW_LC3Volb)
#dunn_test(AveLC3VolPerCell~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

KW_LC3VolMMb<-kruskal_test(LC3VolMinMax~Type, data=temp[temp$BvsS == "Starved",])
summary(KW_LC3VolMMb)
dt_LC3Vols<-dunn_test(LC3VolMinMax~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

#KW_LC3Intb<-kruskal_test(AveLC3IntPerCell~Type, data=temp[temp$BvsS == "Starved",])
#summary(KW_LC3Intb)
#dunn_test(AveLC3IntPerCell~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

KW_LC3IntMMb<-kruskal_test(LC3IntMinMax~Type, data=temp[temp$BvsS == "Starved",])
summary(KW_LC3IntMMb)
dt_LC3Ints<-dunn_test(LC3IntMinMax~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

#KW_LC3SumIntb<-kruskal_test(AveLC3SumIntPerCell~Type, data=temp[temp$BvsS == "Starved",])
#summary(KW_LC3SumIntb)
#dunn_test(AveLC3SumIntPerCell~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

KW_LC3SumIntMMb<-kruskal_test(LC3SumIntMinMax~Type, data=temp[temp$BvsS == "Starved",])
summary(KW_LC3SumIntMMb)
dt_LC3SumInts<-dunn_test(LC3SumIntMinMax~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

#KW_LC3totIntb<-kruskal_test(TotLC3IntPerCell~Type, data=temp[temp$BvsS == "Starved",])
#summary(KW_LC3totIntb)
#dunn_test(TotLC3IntPerCell~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

KW_LC3totIntMMb<-kruskal_test(LC3totIntMinMax~Type, data=temp[temp$BvsS == "Starved",])
summary(KW_LC3totIntMMb)
dt_LC3totInts<-dunn_test(LC3totIntMinMax~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

#KW_LAMPVolb<-kruskal_test(AveLAMPVolPerCell~Type, data=temp[temp$BvsS == "Starved",])
#summary(KW_LAMPVolb)
#dunn_test(AveLAMPVolPerCell~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

KW_LAMPVolMMb<-kruskal_test(LAMPVolMinMax~Type, data=temp[temp$BvsS == "Starved",])
summary(KW_LAMPVolMMb)
dt_LAMPVols<-dunn_test(LAMPVolMinMax~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

#KW_LAMPIntb<-kruskal_test(AveLAMPIntPerCell~Type, data=temp[temp$BvsS == "Starved",])
#summary(KW_LAMPIntb)
#dunn_test(AveLAMPIntPerCell~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

KW_LAMPIntMMb<-kruskal_test(LAMPIntMinMax~Type, data=temp[temp$BvsS == "Starved",])
summary(KW_LAMPIntMMb)
dt_LAMPInts<-dunn_test(LAMPIntMinMax~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

#KW_LAMPSumIntb<-kruskal_test(AveLAMPSumIntPerCell~Type, data=temp[temp$BvsS == "Starved",])
#summary(KW_LAMPSumIntb)
#dunn_test(AveLAMPSumIntPerCell~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

KW_LAMPSumIntMMb<-kruskal_test(LAMPSumIntMinMax~Type, data=temp[temp$BvsS == "Starved",])
summary(KW_LAMPSumIntMMb)
dt_LAMPSumInts<-dunn_test(LAMPSumIntMinMax~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

#KW_LAMPtotIntb<-kruskal_test(TotLAMPIntPerCell~Type, data=temp[temp$BvsS == "Starved",])
#summary(KW_LAMPtotIntb)
#dunn_test(TotLAMPIntPerCell~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")

KW_LAMPtotIntMMb<-kruskal_test(LAMPtotIntMinMax~Type, data=temp[temp$BvsS == "Starved",])
summary(KW_LAMPtotIntMMb)
dt_LAMPtotInts<-dunn_test(LAMPtotIntMinMax~Type, data=temp[temp$BvsS == "Starved",], p.adjust.method = "bonferroni")
```

R-bind and export results from Kruskal-Wallis and Dunn test
```{r}
Dunn_basal<-rbind(dt_LC3Countb, dt_LC3Volb, dt_LC3Intb, dt_LC3SumIntb, dt_LC3totIntb, dt_LAMPVolb, dt_LAMPIntb, dt_LAMPSumIntb, dt_LAMPtotIntb)

Dunn_starved<-rbind(dt_LC3Counts, dt_LC3Vols, dt_LC3Ints, dt_LC3SumInts, dt_LC3totInts, dt_LAMPVols, dt_LAMPInts, dt_LAMPSumInts, dt_LAMPtotInts)

write.csv(Dunn_basal, file= "./Analysis-files/eqCellsum_analysis/stats/Dunn_basal_1Jun21.csv")

write.csv(Dunn_starved, file= "./Analysis-files/eqCellsum_analysis/stats/Dunn_starved_1Jun21.csv")

```





ANOVA of object counts
*multiple replicates*
```{r}
temp$Rep<-as.factor(temp$Rep)

anovaLC3Counts<-aov(temp$LC3PunctaCount~temp$Type*temp$BvsS+temp$Rep+temp$Rep:temp$Type)
summary(anovaLC3Counts)
TukeyHSD(anovaLC3Counts)

anovaLC3CountsMM<-aov(temp$LC3CountMinMax~temp$Type*temp$BvsS+temp$Rep+temp$Rep:temp$Type)
summary(anovaLC3CountsMM)
TukeyHSD(anovaLC3CountsMM)

```

ANOVA of object counts; separate Basal vs Starved analysis
*multiple replicates*
```{r}
#to test segmentation of dataset
#subsetB<-temp[temp$BvsS == "Basal",]

#Basal
anovaLC3CountsBasal<-aov(LC3PunctaCount~Type+Rep, temp[temp$BvsS == "Basal",])

summary(anovaLC3CountsBasal)
TukeyHSD(anovaLC3CountsBasal)

anovaLC3CountsMMbasal<-aov(LC3CountMinMax~Type, temp[temp$BvsS == "Basal",])

summary(anovaLC3CountsMMbasal)
TukeyHSD(anovaLC3CountsMMbasal)

#Starved
anovaLC3CountsStarved<-aov(LC3PunctaCount~Type+Rep, temp[temp$BvsS == "Starved",])

summary(anovaLC3CountsStarved)
TukeyHSD(anovaLC3CountsStarved)

anovaLC3CountsMMstarved<-aov(LC3CountMinMax~Type+Rep, temp[temp$BvsS == "Starved",])

summary(anovaLC3CountsMMstarved)
TukeyHSD(anovaLC3CountsMMstarved)

```

ANOVA of object counts
*1 replicate*
```{r}
anovaLC3Counts<-aov(temp$LC3PunctaCount~temp$Type*temp$BvsS)
summary(anovaLC3Counts)
TukeyHSD(anovaLC3Counts)
```

T-Test of object counts, individual replicates
```{r}
x<-"LC3CountMinMax"
for (t in c("WT", "Control", "tepsin", "AP4E1")) {
  
  s<-temp[[x]][which(temp$BvsS=="Starved" & temp$Type==t)]
  b<-temp[[x]][which(temp$BvsS=="Basal" & temp$Type==t)]
  
  nam<-paste("t",x,t,sep="")
  assign(nam,t.test(s,b))
  }


```

ANOVA of all object metrics
*multiple replicates*
```{r}
temp$Rep<-as.factor(temp$Rep)

#Basal
anovaLC3Vol<-aov(temp$LC3VolMinMax~Type+Rep, temp[temp$BvsS == "Basal",])
summary(anovaLC3Vol)
TukeyHSD(anovaLC3Vol)

anovaBMeanLC3PuncInt<-aov(temp$LC3IntMinMax~Type+Rep, temp[temp$BvsS == "Basal",])
summary(anovaMeanLC3PuncInt)
TukeyHSD(anovaMeanLC3PuncInt)

anovaBSumLC3PuncInt<-aov(temp$LC3SumIntMinMax~Type+Rep, temp[temp$BvsS == "Basal",])
summary(anovaSumLC3PuncInt)
TukeyHSD(anovaSumLC3PuncInt)

anovaBTotLC3Int<-aov(temp$LC3totIntMinMax~Type+Rep, temp[temp$BvsS == "Basal",])
summary(anovaTotLC3Int)
TukeyHSD(anovaTotLC3Int)

anovaBLAMPVol<-aov(temp$LAMPVolMinMax~Type+Rep, temp[temp$BvsS == "Basal",])
summary(anovaLAMPVol)
TukeyHSD(anovaLAMPVol)

#anovaBMeanLAMPPuncInt<-aov(temp$LAMPIntMinMax~Type+Rep, temp[temp$BvsS == "Basal",])
#summary(anovaMeanLAMPPuncInt)
#TukeyHSD(anovaMeanLAMPPuncInt)

anovaBSumLAMPPuncInt<-aov(temp$LAMPSumIntMinMax~Type+Rep, temp[temp$BvsS == "Basal",])
summary(anovaSumLAMPPuncInt)
TukeyHSD(anovaSumLAMPPuncInt)

anovaBTotLAMPInt<-aov(temp$LAMPtotIntMinMax~Type+Rep, temp[temp$BvsS == "Basal",])
summary(anovaTotLAMPInt)
TukeyHSD(anovaTotLAMPInt)


#Starved
anovaSLC3Vol<-aov(temp$LC3VolMinMax~Type+Rep, temp[temp$BvsS == "Starved",])
summary(anovaLC3Vol)
TukeyHSD(anovaLC3Vol)

anovaSMeanLC3PuncInt<-aov(temp$LC3IntMinMax~Type+Rep, temp[temp$BvsS == "Starved",])
summary(anovaMeanLC3PuncInt)
TukeyHSD(anovaMeanLC3PuncInt)

anovaSSumLC3PuncInt<-aov(temp$LC3SumIntMinMax~Type+Rep, temp[temp$BvsS == "Starved",])
summary(anovaSumLC3PuncInt)
TukeyHSD(anovaSumLC3PuncInt)

anovaSTotLC3Int<-aov(temp$LC3totIntMinMax~Type+Rep, temp[temp$BvsS == "Starved",])
summary(anovaTotLC3Int)
TukeyHSD(anovaTotLC3Int)

anovaSLAMPVol<-aov(temp$LAMPVolMinMax~Type+Rep, temp[temp$BvsS == "Starved",])
summary(anovaLAMPVol)
TukeyHSD(anovaLAMPVol)

#anovaSMeanLAMPPuncInt<-aov(temp$LAMPIntMinMax~Type+Rep, temp[temp$BvsS == "Starved",])
#summary(anovaMeanLAMPPuncInt)
#TukeyHSD(anovaMeanLAMPPuncInt)

anovaSSumLAMPPuncInt<-aov(temp$LAMPSumIntMinMax~Type+Rep, temp[temp$BvsS == "Starved",])
summary(anovaSumLAMPPuncInt)
TukeyHSD(anovaSumLAMPPuncInt)

anovaSTotLAMPInt<-aov(temp$LAMPtotIntMinMax~Type+Rep, temp[temp$BvsS == "Starved",])
summary(anovaTotLAMPInt)
TukeyHSD(anovaTotLAMPInt)
```

single replicate ANOVA of Individual Puncta metrics
*for stats of single replicates*
```{r}
#anovaLC3Vol<-aov(temp$AveLC3VolPerCell~temp$Type*temp$BvsS)
#summary(anovaLC3Vol)
#TukeyHSD(anovaLC3Vol)

#anovaMeanLC3PuncInt<-aov(temp$AveLC3IntPerCell~temp$Type*temp$BvsS)
#summary(anovaMeanLC3PuncInt)
#TukeyHSD(anovaMeanLC3PuncInt)

#anovaSumLC3PuncInt<-aov(temp$AveLC3SumIntPerCell~temp$Type*temp$BvsS)
#summary(anovaSumLC3PuncInt)
#TukeyHSD(anovaSumLC3PuncInt)

#anovaTotLC3Int<-aov(temp$TotLC3IntPerCell~temp$Type*temp$BvsS)
#summary(anovaTotLC3Int)
#TukeyHSD(anovaTotLC3Int)

#anovaLAMPVol<-aov(temp$AveLAMPVolPerCell~temp$Type*temp$BvsS)
#summary(anovaLAMPVol)
#TukeyHSD(anovaLAMPVol)

#anovaMeanLAMPPuncInt<-aov(temp$AveLAMPIntPerCell~temp$Type*temp$BvsS)
#summary(anovaMeanLAMPPuncInt)
#TukeyHSD(anovaMeanLAMPPuncInt)

#anovaSumLAMPPuncInt<-aov(temp$AveLAMPSumIntPerCell~temp$Type*temp$BvsS)
#summary(anovaSumLAMPPuncInt)
#TukeyHSD(anovaSumLAMPPuncInt)

#anovaTotLAMPInt<-aov(temp$TotLAMPIntPerCell~temp$Type*temp$BvsS)
#summary(anovaTotLAMPInt)
#TukeyHSD(anovaTotLAMPInt)
```


Use for ANOVA run to cycle through basal and starved separately on single replicates
*need to manually run summary and TukeyHSD*

```{r}
for (b in c("Basal","Starved")) {
    for (x in c("AveLC3VolPerCell","AveLC3IntPerCell","AveLC3SumIntPerCell","TotLC3IntPerCell","AveLAMPVolPerCell","AveLAMPIntPerCell","AveLAMPSumIntPerCell","TotLAMPIntPerCell")){
      for (r in c("1","2","3")) {
  nam<-paste("a",r,b,x,sep="")
  assign(nam,aov(temp[[x]][which(temp$BvsS==b & temp$Rep==r)] ~ temp$Type[which(temp$BvsS==b & temp$Rep==r)]))
  
    }
}
  }
```

Single replicate T-test for analysis of basal versus starved
*visualize in environment tab*
```{r}
for (t in c("WT", "Control", "tepsin", "AP4E1")) {
  for (x in c("AveLC3VolPerCell","AveLC3IntPerCell","AveLC3SumIntPerCell","TotLC3IntPerCell","AveLAMPVolPerCell","AveLAMPIntPerCell","AveLAMPSumIntPerCell","TotLAMPIntPerCell")){
  s<-temp[[x]][which(temp$BvsS=="Starved" & temp$Type==t)]
  b<-temp[[x]][which(temp$BvsS=="Basal" & temp$Type==t)]
  
  nam<-paste("t",x,t,sep="")
  assign(nam,t.test(s,b))
  }
}

```